---
title: "Data Challenge 1: Example"
author: "Will Simmons"
date: "9/28/2021"
output: 
  html_document:
    toc: true 
    toc_float: true
---

[Link to my GitHub repo for this assignment.](https://github.com/simmwill/DSI_Data_Challenge_1)

**NOTE:** The example repository linked above is public so that you can see it as an example, **but all student repositories must be private and shared with instructor and TAs!**

This is an example RMarkdown document. Note that some stylistic choices in this document (e.g., a table of contents) are not required, but feel free to include them in your submission.

### Setup
```{r, message=FALSE}
## load in the required libraries 
library(readr)
library(tidyverse)
library(here)

## read in the data using here() function
state_milk_production <- read_csv(here("data/state_milk_production.csv"))
clean_cheese <- read_csv(here("data/clean_cheese.csv"))
fluid_milk_sales <- read_csv(here("data/fluid_milk_sales.csv"))
milk_products_facts <- read_csv(here("data/milk_products_facts.csv"))
milkcow_facts <- read_csv(here("data/milkcow_facts.csv"))

## disable scientific notation
options(scipen = 999)
```

### Figure 1

```{r}
# make sure to include your code and that it's visible!
```

[figure]

*Figure 1. [write caption]*

### Figure 2

```{r}
# make sure to include your code and that it's visible!
```

[figure]

*Figure 2. [write caption]*

### Figure 3

```{r}
# make sure to include your code and that it's visible!
```

[figure]

*Figure 3. [write caption]*

### Figure 4

```{r}
# make sure to include your code and that it's visible!
```

[figure]

*Figure 4. [write caption]*

### Figure 5

```{r}
# make sure to include your code and that it's visible!
```

[figure]

*Figure 5. [write caption]*
